Optimal (Multiway) Spatial Joins

### 2024-06-03 msj.tex
yufei

\extraspacing {\bf Generating $\bm{\J_2}$.} Take any $(k-1)$-tuple $\bm{t} = (r_1, ..., r_{k-3}, h', v) \in \J(R_1, ..., R_{k-3}, H', V)$. Note that $B_\bm{t}$ --- defined in \eqref{eqn:B_t} --- is a point (due to $h'$ and $v$). Suppose $h' = [x_1, x_2] \times y$ and $B_\bm{t} = (x, y)$, we define the {\em effective horizontal segment} of $\bm{t}$ as the horizontal segment $[x_1, x] \times y$. This allows us to define
\myeqn{
    \contained_{R_{k-2}}(\bm{t}) &=& \{r \in R_{k-2} \mid \text{ the effective horizontal } \nn \\[-1mm]
    && \text{segment of $\bm{t}$ is contained in $r$}   \}
    \label{eqn:type2:contained-t}
}
The above should not be confused with \eqref{eqn:contained}, where the ``$\contained$'' function takes a segment as the parameter, rather than a tuple.

@@

\extraspacing {\underline{\em Example 5.4.}} For $\bm{t}_1 = (\alpha, h_2', v_1)$, first find the full segment of $h_2'$, which is $h_2$. As $\beta_1$ is the only rectangle in $\contained_{R_2}(\bm{t}_1)$, Line 5 of the algorithm adds tuple $(\alpha, \beta_1, h_2, v_1)$ to $\J_2$. For $\bm{t}_2 = (\alpha, h_3', v_1)$, the full segment of $h_3'$ is $h_3$. As $\contained_{R_2}(\bm{t}_2) = \set{\beta_1, \beta_2, \beta_3}$, Line 5 adds $(\alpha, \beta_1, h_3, v_1)$, $(\alpha, \beta_2, h_3, v_1)$, and $(\alpha, \beta_3, h_3, v_1)$ to $\J_2$. Finally, the processing of $\bm{t}_3 = (\alpha, h_3', v_2)$ adds $(\alpha, \beta_3, h_3, v_2)$ to $\J_2$.
\done

>>>>

\extraspacing {\bf Generating $\bm{\J_2}$.} Take any $(k-1)$-tuple $\bm{t} = (r_1, ..., r_{k-3}, h', v) \in \J(R_1, ..., R_{k-3}, H', V)$. Note that $B_\bm{t}$ --- defined in \eqref{eqn:B_t} --- is a point (due to $h'$ and $v$). Suppose $h' = [x_1, x_2] \times y$ and $B_\bm{t} = (x, y)$, we define the {\em effective horizontal segment} of $\bm{t}$ as the horizontal segment $[x_1, x] \times y$. This allows us to define
\myeqn{
    \contained_{R_{k-2}}(\bm{t}) = \{r \in R_{k-2} \mid \text{ the effective horizontal segment of $\bm{t}$ is contained in $r$}   \}
    \label{eqn:type2:contained-t}
}
The above should not be confused with \eqref{eqn:contained}, where the ``$\contained$'' function takes a segment as the parameter, rather than a tuple.

@@

\extraspacing {\underline{\em Example 5.4.}} For $\bm{t}_1 = (\alpha, h_2', v_1)$, the full segment of $h_2'$ is $h_2$. As $\beta_1$ is the only rectangle in $\contained_{R_2}(\bm{t}_1)$, Line 5 of the algorithm adds tuple $(\alpha, \beta_1, h_2, v_1)$ to $\J_2$. For $\bm{t}_2 = (\alpha, h_3', v_1)$, the full segment of $h_3'$ is $h_3$. As $\contained_{R_2}(\bm{t}_2) = \set{\beta_1, \beta_2, \beta_3}$, Line 5 adds $(\alpha, \beta_1, h_3, v_1)$, $(\alpha, \beta_2, h_3, v_1)$, and $(\alpha, \beta_3, h_3, v_1)$ to $\J_2$. Finally, the processing of $\bm{t}_3 = (\alpha, h_3', v_2)$ adds $(\alpha, \beta_3, h_3, v_2)$ to $\J_2$.
\done
